Polynomial Chaos for the Estimation of Manning's Friction

### 2013-11-12 paper/paper.tex
adding inference section
Add formatting for Ocean Modelling

\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{natbib}

\oddsidemargin 0in
\evensidemargin 0in
\textwidth= 6.5in
\topmargin -0.50in
\textheight 9in

\usepackage{latexsym,amssymb,amsmath,color}
\newcommand{\revised}[1]{\textcolor{blue}{{#1}}}
\newcommand{\comment}[1]{\textcolor{red}{{#1}}}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\xxi}{\vec{\xi}}
\newcommand{\xxii}{\xxi^{(\scriptscriptstyle{-}\scriptstyle{i})}}
\newcommand{\var}[1]{{\mathrm{Var}}\left[ {#1} \right]}
\newcommand{\ip}[2]{\left( {#1}, {#2} \right)}
\newcommand{\U}{\mathcal{U}}
\newcommand{\normim}[1]{\left\| {#1} \right\|_{\scriptscriptstyle L^{2}(\Omega^{*})}}
\newcommand{\avemu}[1]{\mathrm{E}\left({#1}\right)}
\newcommand{\ave}[1]{\left\langle {#1} \right\rangle}
\newcommand{\prob}[1]{\mathrm{Prob}\left\{ {#1} \right\}}
\newcommand{\ind}[1]{\mathrm{\chi}_{\scriptscriptstyle {#1} }}
\newcommand{\NISP}{\mathcal{S}}
\newcommand{\ipmu}[2]{\left( {#1}, {#2} \right)_\mu}
\newcommand{\norm}[1]{\left\| {#1} \right\|_{\scriptscriptstyle L^{2}(\Omega)}}
\newcommand{\pard}[2]{\frac{\partial{#1}}{\partial{#2}}}
\def\xbold{{\vec{x}}}
\renewcommand{\vec}[1]{{\mathchoice
                     {\mbox{\boldmath$\displaystyle{#1}$}}
                     {\mbox{\boldmath$\textstyle{#1}$}}
                     {\mbox{\boldmath$\scriptstyle{#1}$}}
                     {\mbox{\boldmath$\scriptscriptstyle{#1}$}}}}
                     %

\begin{document}
\begin{center}{\Large\bf Tsunami Uncertainty Quantification}\vskip 5pt

\bf Preliminary results
\end{center}
\vskip 15pt

@@

\clearpage
%\input{inference}

\input{uqpce}
\input{results}

\clearpage

\clearpage
\bibliographystyle{plainnat}
\bibliography{biblio}
\end{document}

>>>>

%&pdflatex
%
%
%
%

% \documentclass[12pt]{article}
\documentclass[preprint,12pt]{elsarticle}

\usepackage{graphicx}
\usepackage{bm}
\usepackage{natbib}

% Add line numbers
\usepackage[mathlines]{lineno}

% Multipart figures
\usepackage{subcaption}

% \oddsidemargin 0in
% \evensidemargin 0in
% \textwidth= 6.5in
% \topmargin -0.50in
% \textheight 9in

\usepackage{ifpdf}

\usepackage{latexsym,amssymb,amsmath,color}
\newcommand{\revised}[1]{\textcolor{blue}{{#1}}}
\newcommand{\comment}[1]{\textcolor{red}{{#1}}}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\xxi}{\vec{\xi}}
\newcommand{\xxii}{\xxi^{(\scriptscriptstyle{-}\scriptstyle{i})}}
\newcommand{\var}[1]{{\mathrm{Var}}\left[ {#1} \right]}
\newcommand{\ip}[2]{\left( {#1}, {#2} \right)}
\newcommand{\U}{\mathcal{U}}
\newcommand{\normim}[1]{\left\| {#1} \right\|_{\scriptscriptstyle L^{2}(\Omega^{*})}}
\newcommand{\avemu}[1]{\mathrm{E}\left({#1}\right)}
\newcommand{\ave}[1]{\left\langle {#1} \right\rangle}
\newcommand{\prob}[1]{\mathrm{Prob}\left\{ {#1} \right\}}
\newcommand{\ind}[1]{\mathrm{\chi}_{\scriptscriptstyle {#1} }}
\newcommand{\NISP}{\mathcal{S}}
\newcommand{\ipmu}[2]{\left( {#1}, {#2} \right)_\mu}
\newcommand{\norm}[1]{\left\| {#1} \right\|_{\scriptscriptstyle L^{2}(\Omega)}}
\newcommand{\pard}[2]{\frac{\partial{#1}}{\partial{#2}}}
\def\xbold{{\vec{x}}}
\renewcommand{\vec}[1]{{\mathchoice
                     {\mbox{\boldmath$\displaystyle{#1}$}}
                     {\mbox{\boldmath$\textstyle{#1}$}}
                     {\mbox{\boldmath$\scriptstyle{#1}$}}
                     {\mbox{\boldmath$\scriptscriptstyle{#1}$}}}}

\newcommand{\geoclaw}{{\sc GeoClaw}\xspace}
\newcommand{\tohoku}{T\={o}hoku\xspace}

\journal{Ocean Modelling}

\begin{document}

\ifpdf
\DeclareGraphicsExtensions{.pdf, .png, .jpg, .tif}
\else
\DeclareGraphicsExtensions{.png, .jpg, .tif, .eps}
\fi

\begin{frontmatter}

\title{Polynomial Chaos for the Estimation of Manning's Friction}
\date{\today}

\author[kaust]{Ihab Sraj}
\ead{ihab.sraj@kaust.edu.sa}
\ead{Department of Physical Sciences and Engineering, King Abdullah University for Science and Technology, Thuwal, Saudi Arabia}
\author[ut]{Kyle T. Mandli}
% \ead{kyle@ices.utexas.edu}
% \ead[http://users.ices.utexas.edu/~kyle]{http://users.ices.utexas.edu/~kyle}
\author[kaust]{Ibrahim Hoteit}
\author[ut]{Clint N. Dawson}

\address[kaust]{Department of Physical Sciences and Engineering, King Abdullah University for Science and Technology, Thuwal, Saudi Arabia}
\address[ut]{Institute for Computational Engineering and Science, University of Texas at Austin, 201 E 24th ST. Stop C0200, Austin, TX 78712-1229, USA}

\date{\today}

\begin{abstract}

\end{abstract}

\begin{keyword}
tsunami \sep Manning's N friction \sep sensitivity analysis \sep polynomial chaos
\end{keyword}

\end{frontmatter}
\linenumbers

% \input{cover}
% \clearpage

@@

\input{formulation}

\input{results}

\input{figures} 
\clearpage

\clearpage
\bibliographystyle{elsarticle-num}
\bibliography{biblio}
\end{document}
